---
output:
  pdf_document: default
  html_document: default
---

Part A: 
  Set seed and take random sample of 25 observations.
  Find the mean Glucose and highest Glucose values from sample and compare with population statistics using    charts.

Mean Glucose from sample:     122.68
Mean Glucose from population: 121.66

Max Glucose from sample:     181
Max Glucose from population: 199
  
```{r}
df <- read.csv("/cloud/project/data/diabetes_clean.csv")
set.seed(1)

# create sample of 25
df_25 <- df %>%
  slice_sample(n=25)

# print summary statistics for sample 
df_25 %>%
  skim(Glucose)

# print summary statistics for population 
df %>%
  skim(Glucose)
```

Part A Charts
```{r}
chart.Boxplot(df_25$Glucose, ylim=c(20,200), main="Sample Glucose Boxplot", xlab="")
chart.Boxplot(df$Glucose, ylim=c(20,200), main="Population Glucose Boxplot", xlab="")
```
  
Part B:
  Find the 98th percentile of BMI and of the sample and population and compare using charts
  
Sample BMI 98th Percentile:    46.08
Population BMI 98th Percentil: 47.526

```{r}
df_25 %>%
  summarize(sample_q98 = quantile(BMI, p=0.98))

df %>%
  summarize(population_q98 = quantile(BMI, p=0.98))
```
Part B Charts
```{r}
# axes are made the same to make for easy comparison. 
# outliers are removed from population plot for better comparison, they are >98th percentile
chart.Boxplot(df_25$BMI, main="Sample BMI", xlab="", ylim=c(10,50))
chart.Boxplot(df$BMI, main="Population BMI", xlab="", ylim=c(10,50), outline=FALSE)
```



Part C:
  Using bootstrap (replace= True), create 500 samples (of 150 observation each) from the
  population and find the average mean, standard deviation and percentile for BloodPressure and
  compare this with these statistics from the population for the same variable. Again, you should
  create charts for this comparison. Report on your findings.
```{r}
num_trials <- 500
n <- 150
df_bp <- 1:num_trials %>%
  map_dfr(
    ~ df %>%
      slice_sample(n = n, replace = TRUE) %>%
      summarize(mean_bp = mean(BloodPressure))
  ) %>%
  mutate(n = n)

df_bp %>%
  skim(mean_bp)

df %>%
  skim(BloodPressure)
```
  
  Part C Charts
```{r}
# scale of axes are not kept the same due to the significant difference in variation
chart.Boxplot(df_bp$mean_bp, main="Bootstrap Blood Pressure", xlab="", outline=FALSE)
chart.Boxplot(df$BloodPressure, main="Population Blood Pressure", xlab="", outline=FALSE)
```
  