Import and Preview Raw Data
```{r}
df_raw <- read.csv("/cloud/project/data/diabetes.csv")
str(df_raw)

# observe distribution of raw data for missing data/outliers
skim(df_raw$Pregnancies)
skim(df_raw$Glucose)
skim(df_raw$BloodPressure)
skim(df_raw$SkinThickness)
skim(df_raw$Insulin)
skim(df_raw$BMI)

```

For cleaning, check for NA's and drop rows with 0's in the three variables we are concerned with in analysis so we can compute values to impute
```{r}
table(is.na(df_raw)) 
df_no_zeroes <- df_no_zeroes[df_no_zeroes$Glucose != 0 & df_no_zeroes$BloodPressure != 0 & df_no_zeroes$BMI != 0,]

# observe distribution of data with zeroes removed
skim(df_no_zeroes$Glucose)
skim(df_no_zeroes$BMI)
skim(df_no_zeroes$BloodPressure)
```

Compute medians and impute for zeroes in raw data
```{r}
median_glucose <- median(df_no_zeroes$Glucose)
median_bmi <- median(df_no_zeroes$BMI)
median_bp <- median(df_no_zeroes$BloodPressure)

df_clean <- df_raw

# impute median for 0's
df_clean$Glucose[df_clean$Glucose == 0] <- median_glucose
df_clean$BMI[df_clean$BMI == 0] <- median_bmi
df_clean$BloodPressure[df_clean$BloodPressure == 0] <- median_bp

# observe distribution of data with imputation
skim(df_clean$Glucose)
skim(df_clean$BMI)
skim(df_clean$BloodPressure)
```

Export cleaned data to be used in analysis.
Note: further imputation/dropping of rows may be necessary for additional analysis. With limited knowledge of how the data was collected/the significance of the values, imputation is done significant attention was paid only to the variables to be analyzed in the assignment.
```{r}
write.csv(df_clean, file="/cloud/project/data/diabetes_clean.csv")
```



